A Critical Review of Sophistication and Algorithmic Model Selection

### 2015-01-06 Facticity/Facticity/paper.tex
added playground

\title{A Critical Review of Sophistication and Algorithmic Model Selection}
\author{Peter Bloem and Steven de Rooij}

@@

>>>>

\title{A Critical Review of Sophistication and Algorithmic Model Selection}

\author{Peter Bloem and Steven de Rooij}

@@

\section{Steven's playground}

Potential alternative title: ``Four problems with all current attempts to define meaningful information''

Requirements for sophistication:

(1) Being an information measure, the value should count the number of bits required for an effective description of the meaningful properties of a binary object.

(2) The Invariance Theorem for Kolmogorov complexity states that a change in reference UTM can only influence the complexity up to an additive constant term. Analogously, if sophistication is to be interpreted as an objective property of the data, then there should be strict limits on the degree to which a change in the UTM can affect the sophistication.

(3) Sophistication should not be $\gamma$-equivalent to 0. While a valid information measure, the function 0 is clearly at odds with the intuition that there is no universal cap on the amount of meaningful information in the world.

(4) Sophistication should not be $\gamma$-equivalent to the Kolmgorov complexity, because then there is no point in defining a new word for the same concept. Moreover, Kolmogorov complexity is at odds with the intuition that there is no meaningful information in a random string.
